Synthesizing Quotient Lenses

### 2017-10-18 papers/QuotientLensSynth/main.tex

The expression \cd{project [ \\n\\t\\r]+ -> " "} is a QRE that matches any 
number of whitespace characters, and then considers all strings of whitespace
characters as equivalent with a single space as the canonical representative. 
Another QRE in the example above is the

>>>>

The expression \cd{project [\n\t\r]}$^+$ $\to$ \cd{" "} is a QRE that matches any 
number of whitespace characters, and then considers all strings of whitespace
characters as equivalent with a single space as the canonical representative. 
Another QRE in the example above is the
